---
title: "Stat 433 Wk2 Hw"
author: "Nick Bowe"
date: "9/28/2021"
output: github_document
---

#1. How many flights have a missing dep_time? What other variables are missing? What might these rows represent?

```{r}
library(nycflights13)
library(dplyr)
library(ggplot2)

filter(flights, is.na(dep_time)) %>% View
#There are 8,255 entries, therefore there are 8,255 flights without departure times.

#Other rows that are missing variables include, arr_time, air_time, and various variables that rely on those two having values. This could be due to the fact that a flight was either cancelled before it had the opportunity to take off, or perhaps was rerouted while in the air meaning the flight was not recorded.

```

#2 Currently dep_time and sched_dep_time are convenient to look at, but hard to compute with because they’re not really continuous numbers. Convert them to a more convenient representation of number of minutes since midnight.

```{r}
flightb = flights %>% 
  mutate(dep_time = 2400 - dep_time) %>% 
  mutate(sched_dep_time = 2400 - sched_dep_time)

head(flightb %>% select(dep_time, sched_dep_time))

```

#3 Look at the number of canceled flights per day. Is there a pattern? Is the proportion of canceled flights related to the average delay? Use multiple dyplr operations, all on one line, concluding with ggplot(aes(x= ,y=)) + geom_point()

```{r}
not_cancelled = flights %>%
  filter(!is.na(dep_delay), !is.na(arr_delay))

not_cancelled %>% 
  group_by(tailnum) %>% 
  summarise(
    delay = mean(arr_delay, na.rm = TRUE),
    n = n()
  ) %>% 
  ggplot(mapping = aes(y = n, x = delay)) + 
  geom_point()


# Unsure how to really flesh out this thought???

```


